favgenes

### 2019-11-13 analysis/12_favegenes.Rmd
new plots with manipluation and candidate genes

plotwidedata <- function(whichgene, myylab){
p <- ggplot(widecountdata, (aes(x = treatment, y = whichgene))) +
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(outlier.color = treatment, fill = treatment, alpha = sex)) +
    mytheme() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(x = NULL, y = myylab) +
    guides(fill = guide_legend(order=1),
         color = guide_legend(order=2)) +
    scale_alpha_manual(values = c(0.75,1)) 
return(p)
}

a <- plotwidedata(widecountdata$PRL, "PRL")
b <- plotwidedata(widecountdata$COX1, "COX1")
c <- plotwidedata(widecountdata$FOSL2, "FOSL2")

plot_grid(a + theme(axis.text.x = element_blank()),c, 
          nrow = 2)
b
```

```{r DESeq2-partialmanip}

PRLremove <- widecountdata %>% 
    filter( !treatment %in% c("m.inc.d8", "prolong", "extend"))  %>% 
  ggplot(aes(x = treatment, y = PRL, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL expression", x = NULL,
         subtitle = "PRL in female and male pituitary") +
    annotate("rect", xmin = 3.7, xmax = 5.3, ymin = 14.5, ymax = 14.6, alpha = 1) +
    annotate("rect", xmin = 5.7, xmax = 7.3, ymin = 14.5, ymax = 14.6, alpha = 1) +
    annotate("rect", xmin = 7.7, xmax = 9.3, ymin = 14.5, ymax = 14.6, alpha = 1) +
    annotate("rect", xmin = 9.7, xmax = 11.3, ymin = 14.5, ymax = 14.6, alpha = 1)

@@

png('../figures/favegenes/PRLtiming.png',width=600,height=400, units="px")
print(PRLtiming)
dev.off()
```

>>>>

plotwidedata <- function(whichgene, myylab){
p <- ggplot(widecountdata, (aes(x = treatment, y = whichgene))) +
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(outlier.color = treatment, fill = treatment, alpha = sex)) +
    mytheme() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(x = NULL, y = NULL, subtitle = myylab) +
    guides(fill = guide_legend(order=1),
         color = guide_legend(order=2)) +
    scale_alpha_manual(values = c(0.75,1)) 
return(p)
}

plotwidedata(widecountdata$PRL, "PRL")

a <- plotwidedata(widecountdata$PRL, "PRL")
b <- plotwidedata(widecountdata$FOSL2, "FOSL2")
c <- plotwidedata(widecountdata$COX1, "COX1")
d <- plotwidedata(widecountdata$BRCA1, "BRCA1")
e <- plotwidedata(widecountdata$CDK1, "CDK1")
f <-plotwidedata(widecountdata$MYC, "MYC")

plot_grid(a + theme(axis.text.x = element_blank()),
          b + theme(axis.text.x = element_blank()),
          c + theme(axis.text.x = element_blank()),
          d + theme(axis.text.x = element_blank()),
          e + theme(axis.text.x = element_blank()),
          f + theme(axis.text.x = element_blank()), nrow = 2)

plot_grid(a + theme(axis.text.x = element_blank()),
          d + theme(axis.text.x = element_blank()),
          e + theme(axis.text.x = element_blank()), nrow = 1)
```

```{r DESeq2-partialmanip}
PRLremove <- widecountdata %>% 
    filter( !treatment %in% c("m.inc.d8", "prolong", "extend"))  %>% 
  ggplot(aes(x = treatment, y = PRL, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL expression", x = NULL,
         subtitle = "PRL in female and male pituitary") +
    annotate("rect", xmin = 3.7, xmax = 5.3, ymin = 14.5, ymax = 14.6, alpha = 1) +
    annotate("rect", xmin = 5.7, xmax = 7.3, ymin = 14.5, ymax = 14.6, alpha = 1) +
    annotate("rect", xmin = 7.7, xmax = 9.3, ymin = 14.5, ymax = 14.6, alpha = 1) +
    annotate("rect", xmin = 9.7, xmax = 11.3, ymin = 14.5, ymax = 14.6, alpha = 1)

@@

png('../figures/favegenes/PRLtiming.png',width=600,height=400, units="px")
print(PRLtiming)
dev.off()

removal <- widecountdata %>% 
    filter( !treatment %in% c("m.inc.d8", "prolong", "extend",  "control", "bldg" , "lay", "n5", "n9"))

plotremove <- function(whichgene, myylab){
  p <-  removal  %>% 
  ggplot(aes(x = treatment, y = whichgene, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = NULL, subtitle = myylab, x = NULL) 
  return(p)
}

a <- plotremove(removal$PRL, "PRL")
b <- plotremove(removal$FOSL2, "FOSL2")
c <- plotremove(removal$COX1, "COX1")
d <- plotremove(removal$BRCA1, "BRCA1")
e <- plotremove(removal$CDK1, "CDK1")
f <- plotremove(removal$MYC, "MYC")

plot_grid(a + theme(axis.text.x = element_blank()),
          d + theme(axis.text.x = element_blank()),
          e + theme(axis.text.x = element_blank()), nrow = 1)

timing <- widecountdata %>% 
    filter( !treatment %in% c("m.inc.d3", "m.inc.d9", "m.inc.d17","m.n2", 
                              "control", "bldg" , "lay", "n5", "n9"))

plottiming <- function(whichgene, myylab){
  p <-  timing  %>% 
  ggplot(aes(x = treatment, y = whichgene, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = NULL, subtitle = myylab, x = NULL) 
  return(p)
}

a <- plottiming(timing$PRL, "PRL")
b <- plottiming(timing$FOSL2, "FOSL2")
c <- plottiming(timing$COX1, "COX1")
d <- plottiming(timing$BRCA1, "BRCA1")
e <- plottiming(timing$CDK1, "CDK1")
f <- plottiming(timing$MYC, "MYC")

plot_grid(a + theme(axis.text.x = element_blank()),
          d + theme(axis.text.x = element_blank()),
          e + theme(axis.text.x = element_blank()), nrow = 1)
